Is high social class always beneficial for survival? Northern Sweden 1801--2013

### 2017-11-28 article4.Rmd
first commit

```{r readalldata}
source("R/get.file.R")
skel <- get.file("skel")
##
skume <- get.file("skume")
##
foli <- get.file("foli")
skel$urban <- FALSE
vb0Tab <- rbind(skel, skume[, names(skel)], foli[, names(skel)])
vb0Tab$civst <- relevel(vb0Tab$civst, ref = "married")
vb0Tab <- aggregate(vb0Tab[, c("event", "exposure")],
                    vb0Tab[, c("sex", "age", "period", "cohort", "civst", "hisclass", "urban")],
                    FUN = sum)
```

@@

```{r hazcalw}
source("R/getPHglm2.R")
source("R/getPHglm.R")
##nper <- 4
nper <- length(labb)
resw <- getPHglm(vb4064[vb4064$sex == "female", ],
            nper, labb)
resm <- getPHglm(vb4064[vb4064$sex == "male", ],
            nper, labb)
```

>>>>

```{r readalldata}
source("R/get.file.R")
skel <- get.file("skel")
##
skume <- get.file("skume")
##
foli <- get.file("foli")
skel$urban <- FALSE
vb0Tab <- rbind(skel, skume[, names(skel)], foli[, names(skel)])
vb0Tab$civst <- relevel(vb0Tab$civst, ref = "married")
vb0Tab <- aggregate(vb0Tab[, c("event", "exposure")],
                    vb0Tab[, c("sex", "age", "period", "cohort", "civst", "hisclass", "urban")],
                    FUN = sum)
vb0Tab$hisclass <- relevel(vb0Tab$hisclass, ref = "middle")
```

@@

```{r hazcalw}
source("R/preg.R")
##nper <- 4
nper <- length(labb)
resw <- matrix(0, nrow = 4, ncol = nper)
resm <- matrix(0, nrow = 4, ncol = nper)
for (i in 1:nper){
  resw[, i] <- preg("+ civst", data = vb4064[vb4064$sex == "female" &
                                               vb4064$period == labb[i], ])
    resm[, i] <- preg("+ civst", data = vb4064[vb4064$sex == "male" &
                                               vb4064$period == labb[i], ])
}
##resw <- getPHglm(vb4064[vb4064$sex == "female", ],
##            nper, labb)
##resm <- getPHglm(vb4064[vb4064$sex == "male", ],
##            nper, labb)
```
